---
title: "Graphics and Visualization"
author: "Chetan"
date: "10/11/2021"
output: word_document
---
#For Accessing all the inbuilt datasets in the R.
```{r}
# ls(package:datasets) 
```

#For Loading datasets
```{r}
 # data("name of the dataset") 

```

#For Accessing  the Attributes in the datasets in the R.
```{r}
# attributes("name of the dataset")

```

#For Accessing the Attiributes of the perticular columns of dataset in the R.
```{r}
# attributes("name of the dataset$perticular col name") 

```

#Line Chart.
```{r}
x=c(14,22,8,19,42)
y=c(12,23,45,23,23)
plot(y,type="o",col="red",xlab="Months",ylab="rain Fall",main="Rain Fall Chart")


```

#Multiple Line Chart
```{r}
x=c(14,22,8,19,42)
y=c(12,23,45,23,23)
plot(y,type="o",col="red",xlab = "Months",ylab="rain Fall",main="Rain Fall chart")
lines(x,type="o",col="blue")

```
#Barplot
```{r}
x=c(122,345,567,987,234,546,677,980,334,147,890,444)
m=month.name
barplot(x,names.arg = m,col=7,xlab ="Months",ylab="Revenue",main="Revenue Vs Months")

```
#Multiple Barplot
```{r}
color=c("red","yellow","blue")
States=c("Maharastra","Rajasthan","kerala")
years=c(month.name[1:5])
high_temp=matrix(c(35,40,31,43,51,39,48,52,42,45,48,39,34,39,37),nrow=3)
b=barplot(high_temp,names.arg=years,xlab="years",ylab="max temeparature",main="Max temp of the states 2015-2021",col=color)
legend("topright",States,cex=0.5,fill = color)


```
#Histogram
```{r}
data("airquality")
# attributes(airquality)
hist(airquality$Temp,xlab="Temperature",ylab="frequency count",col=6,main="Histogram of temperature in airqulality dataset",probability = TRUE)
# to draw the density line we have to add probability= TRUE in hist() function.
lines(density(airquality$Temp))
```
#using breaks command.
```{r}
#without breaks
hist(cars$dist)
```


```{r}
# with breaks command
data("cars")
brk=seq(0,120,5)
hist(cars$dist,main="Distance",breaks = brk,probability = TRUE)

lines(density(cars$dist))
```
#Scatter Plot.

```{r}
x=seq(1,50,5)
y=seq(2,51,5)
par(mfrow=c(2,2))
plot(x,y,type="o")
plot(x,y,type="l")
plot(x,y,type="b")
plot(x,y,type="c")
```

```{r}
data("airquality")
par(mfrow=c(2,2))
plot(airquality$Temp,airquality$Ozone,col="red")
plot(airquality$Temp,airquality$Ozone,col="blue",type="b")
plot(airquality$Temp,airquality$Ozone,col="yellow",type="c")
plot(airquality$Temp,airquality$Ozone,col="black",type="l")


```
#Dotplot/Dotchart
```{r}
# a dot chart or dot plot is same as the scatter plot. the main difference is that the dot plot in R displays the index(each category) in vertical axis and the corresponding value in the horizontal axis.
```

```{r}
data("cars")
plot(cars$dist,cars$speed,main="Distance Vs Speed" )

```

#Boxplot
```{r}
data("sleep")
# sleep$extra~sleep$group :y axis on x axis
boxplot(sleep$extra~sleep$group,xlab="group no.",ylab="Extra sleeping hours",main="boxplot comparing Numetical data with categorical data")

```
#Pie Chart.
```{r}

States_label=c("Maharastra","Kerala","Tamilnadu","Bihar","jharkhand","Lakshdweep")
literacy=c(82,94,80,61,66,91)
label=round(c(100*literacy/sum(literacy),1))
pie(literacy,labels =paste0(label,"%"),main="Pie Chart Of the no of college of States",col=rainbow(length(literacy)))
legend("topright",States_label,fill=rainbow(length(literacy)))

```
#labeling count with percentages.
```{r}
States_label=c("Maharastra","Kerala","Tamilnadu","Bihar","jharkhand","Lakshdweep")
literacy=c(82,94,80,61,66,91)
label=round(c(100*literacy/sum(literacy),1))
pie(literacy,labels =paste(literacy,"=",label,"%"),main="Pie Chart Of the no of college of States",col=rainbow(length(literacy)))
legend("topright",States_label,fill=rainbow(length(literacy)))
```
#Pie chart with categorical data.
```{r}
gender=factor(c(rep("Male",10), rep("Female",20)))
pie(table(gender),main = "Male and Female ",col =c(5,7))
legend("topright",c("Male","Famale"),fill = c(5,7))

```
#Pairs Plot.
```{r}
data("airquality")
pairs(airquality)
```
#Stem-Leaf Plot:
```{r}
# A Stem and Leaf Diagram, also called Stem and Leaf plot in R, is a 
# special table where each numeric value split into a stem (First digit(s) ) and a leaf (last 
# Digit). Stem and Leaf plot is a technique of displaying the frequencies with which some 
# classes of values may occur.
data("iris")
stem(iris$Petal.Length)

```
#3D -Plots
```{r}
library(plotrix)
countries=c("United States","China","Japan","Germany","U.k","France","India","Italy")
gdp=c(20.49,13.4,4.97,4,2.83,2.78,2.72,2.070)
pie3D(gdp,labels=countries,main="GDP of top coounties",col=c(2:9))
legend("topleft",countries,fill = c(2:9),cex = 0.6)


```

