---
title: "import_export"
author: "Chetan Salunke"
date: "30/10/2021"
---

#Comment: "Get Working_directory"
```{r}
getwd()
```
#Importing the csv files in R from the current working dirctory:

```{r}
df=read.csv("BOOk2.csv",header = TRUE);df
```

#Importing csv file using the location path of the file:

```{r}
df1=read.csv("C:/Users/DELL/OneDrive/Desktop/Sample_data.csv")
head(df1)
```
#Importing the Delimited file in the R:
If a file with a separator character that is different from a 
tab, a comma or a semicolon, you can always use the.
```{r}
df2=read.delim("C:/Users/DELL/OneDrive/Documents/data.txt",header=FALSE,sep="")
head(df2)
```
##importing Text File in the R:
If a file with a separator character that is a 
tab, a comma or a semicolon, you can always use the.
```{r}
df=read.table("C:/Users/DELL/OneDrive/Desktop/table.txt",header=FALSE)
df

```
#import Excel file into the R:
```{r}
library(readxl)
df=read_excel("C:/Users/DELL/OneDrive/Documents/Excel Files/Tutorial5.xlsx");df
```
#skip rows and use default columns name
```{r}
library(readxl)
df=read_excel("C:/Users/DELL/OneDrive/Documents/Excel Files/Tutorial5.xlsx",skip=1,col_names = FALSE)

```
#Exporting files in the R:
1)Exporting the CSV
```{r}
library(dplyr)
  df=mtcars %>%
  select(mpg,disp,gear)%>%
  group_by(gear) %>%
  summarize(mean_mpg=mean(mpg),mean_disp=mean(disp))
  write.csv(df,"table_cars")
```
#export Excel file
```{r}
library(xlsx)
write.xlsx(df,"excel_table_cars")
```
#Some important functions in the R:
#1)Cat Function:
i)returns character string in the readable format.
ii)combine character values and print them to the screen.
iii) Let understand the difference between cat and print function.
```{r}
str="Chetan Rajaram Salunke"
print(str)
cat(str)
s="Programming with data \n is fun"
cat(s)
cat(s,"with R")
```

```{r}
cat(1:12,sep = "_")
print("\n")
cat(month.name[1:4],sep = "-")
```

```{r}
m=matrix(1:9,byrow=TRUE,nrow=3)
print("print using print function")
print(m)
cat("print using cat funtion \n",m)
```

#2)Sink function:
Export(Write) the data in multiple forms such as text and CSV files.
#As Text File:
```{r}
df=datasets::airquality
sink("C:/Users/DELL/OneDrive/Documents/R-Studio/summary_airquality.txt")
summary(df)
``` 
#AS CSV File:
```{r}
df1=datasets::cars    #or data(cars)
sink( "C:/Users/DELL/OneDrive/Documents/R-Studio/cars.csv")
df1
sink()
```
#3)Format Fucntion.
This is especially useful when printing numbers and quantities under 
different formats.

```{r}
format(160.234569)
format(13.7,nsmall=3)
```


```{r}
d=diag(5);d
 
```
#to find the inverse of the matrix


```{r}
a=matrix(c(3,2,3,8),byrow = TRUE,ncol=2);a
det(a)
solve(a)
```











